Modeling memory and taxis to analyze migrations

### 2021-01-15 code/StrategicVsTactical_PartI_v2.Rmd
fixed code for pulsed resource

R2 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 9, x.peak = 80, x.sd = 5))
R3 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 5, x.peak = 80, x.sd = 9))
R4 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 5, x.peak = 80, x.sd = 5))

par(mfrow = c(2,2), mar = c(3,3,3,1), mgp = c(2,.25,0), las = 1, tck = 0.01)
with(world.R1, {     
  image(1:tau,X.mid,resource, main = "Broad, long peak")
  contour(1:tau,X.mid,resource, add = TRUE)
  })

image(Time,X,R2, main = "Narrow, long peak"); contour(Time,X,R2, add = TRUE)
image(Time,X,R3, main = "Broad, short peak"); contour(Time,X,R3, add = TRUE)
image(Time,X,R4, main = "Narrow, short peak"); contour(Time,X,R4, add = TRUE)
```

# Running the model in a seasonal environment

@@

```{r PulseSim1, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2)
Memory_PulsedResource_Sim <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

@@

```{r PulseSim2, fig.width = 10}
parameters <- c(epsilon = 2, alpha = 4e2, beta = 0, lambda = 0, dx = dx)
Tactic_PulsedResource_Sim <- runManyYears(pop.Year1, Time, 
                                  Resource = R1, Parameters = parameters, n.years = 6)
par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Tactic_PulsedResource_Sim, tau = tau)
plotYearList(Tactic_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim3, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta = 3e2, lambda = 0, dx = dx)
Hybrid_PulsedResource_Sim <- runManyYears(pop.Year1, Time, 
                                  Resource = R1, Parameters = parameters, n.years = 6)
par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim4_tactic, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta = 0, lambda = 0, dx = dx)
Hybrid_PulsedResource_Sim2 <- runManyYears(pop.Year1, Time, 
                                  Resource = R4, Parameters = parameters, n.years = 6)
par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim2, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim2, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim4_memory, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta = 3e2, lambda = 0, dx = dx)
Hybrid_PulsedResource_Sim2 <- runManyYears(pop.Year1, Time, 
                                  Resource = R4, Parameters = parameters, n.years = 6)
par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim2, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim2, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

>>>>

world.R2 <- world %>% 
  list_modify(resource = getPulsedResource(1:world$tau, world$X.mid, c(t.peak = 25, t.sd = 9, x.peak = 80, x.sd = 5)))

world.R3 <- world %>% 
  list_modify(resource = getPulsedResource(1:world$tau, world$X.mid, c(t.peak = 25, t.sd = 5, x.peak = 80, x.sd = 9)))

world.R4 <- world %>% 
  list_modify(resource = getPulsedResource(1:world$tau, world$X.mid, c(t.peak = 25, t.sd = 5, x.peak = 80, x.sd = 5)))

par(mfrow = c(2,2), mar = c(3,3,3,1), mgp = c(2,.25,0), las = 1, tck = 0.01)
with(world.R1, {     
  image(1:tau,X.mid,resource, main = "Broad, long peak")
  contour(1:tau,X.mid,resource, add = TRUE)
  })
with(world.R2, {     
  image(1:tau,X.mid,resource, main = "Narrow, long peak")
  contour(1:tau,X.mid,resource, add = TRUE)
  })
with(world.R3, {     
  image(1:tau,X.mid,resource, main = "Broad, short peak")
  contour(1:tau,X.mid,resource, add = TRUE)
  })
with(world.R4, {     
  image(1:tau,X.mid,resource, main = "Narrow, short peak")
  contour(1:tau,X.mid,resource, add = TRUE)
  })

# Running the model in a seasonal environment
# Note: to view any of the resource models, change the world

@@

```{r PulseSim1, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2)
Memory_PulsedResource_Sim <- runManyYears(world.R3, Parameters = parameters, n.years = 6)

@@

```{r PulseSim2, fig.width = 10}
parameters <- c(epsilon = 2, alpha = 4e2, beta0 = 0, beta1 = 0)
Tactic_PulsedResource_Sim <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Tactic_PulsedResource_Sim, tau = tau)
plotYearList(Tactic_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim3, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta0 = 20, beta1 = 3e2)
Hybrid_PulsedResource_Sim <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)

@@

```{r PulseSim4_tactic, fig.width = 10}
parameters <- c(epsilon = 2, alpha = 2e2, beta0 = 0, beta1 = 0)
Tactic_PulsedResource_Sim2 <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim2, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim2, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim4_memory, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta0 = 20, beta1 = 3e2)
Hybrid_PulsedResource_Sim3 <- runManyYears(world.R4, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim3, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim3, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```
